X-ray phase-contrast imaging at \SI{100}{\kilo\electronvolt}

### 2013-09-03 natphys/hedpc_natphys.tex
Marco's revision
- changed revtex output to double spaced one column
- compact setup in the abstract
- cite Ruiz poster on GI @123 keV at ESRF
- removed comments on the max energy of recent experiments other than GI at
  synchrotron or table top sources
- phase nature rather than differential nature of the DPC
- updated caption of chip image to include differential abs
- added comment on long exposure due to low visibility
- added grant in the acknowledgements

%\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress,groupedaddress]{revtex4}
%% for review and submission
%\documentclass[aps,preprint,showpacs,superscriptaddress,groupedaddress]{revtex4}
% for double-spaced preprint
%\documentclass[aps,prl,floatfix,twocolumn,10pt]{revtex4-1}
%for review and submission
%\documentclass[aps,prl,preprint]{revtex4-1} 
% for double-spaced preprint
%\documentclass[aip,apl,amsmath,amssymb,floatfix,preprint,a4paper]{revtex4-1}
\documentclass[aip,apl,amsmath,amssymb,floatfix,reprint,a4paper]{revtex4-1}

@@

%% ----------------------------------------------------------------------------------------------------------------
\begin{abstract}
    Phase contrast imaging with X-rays provides access to
    complementary physical contrast mechanisms. Phase sensitive imaging in
    the diagnostic energy range between $80$ and
    $\SI{150}{\kilo\electronvolt}$ is still largely unexplored, as the
    current methods typically entail severe technical challenges. A
    phase-contrast technique at such high energies is of scientific and
    industrial interest as it vastly expands the range of applications, for
    instance, by the examination of materials of high density or thickness.
    The approach includes a new design for the grating manufacturing in
    Talbot-Lau interferometry, with an edge-on illumination and curved
    structures to match the beam divergence. The edge-on approach breaks the
    current limits of achievable grating aspect ratios, which has been a key
    issue for a long time. The curvature of the gratings solves the
    intrinsic reduction of the field of view which occurs for gratings with
    such high aspect ratios. Using an imaging arrangement based on a
    conventional X-ray tube, phase and dark-field contrast imaging at
    $\SI{100}{\kilo\electronvolt}$ is demonstrated. This achievement paves
    the road for the transfer of phase-contrast imaging into fields where
    high energies are required, such as medical computed tomography, chip
    failure analysis or homeland security.
\end{abstract}

@@

Phase-contrast imaging has so far been used in the energy
range from $15$ up to $\SI{85}{\kilo\electronvolt}$. Talbot
interferometry has been demonstrated using a synchrotron source at
$\SI{82}{\kilo\electronvolt}$ \cite{Willner2013}. Also using a synchrotron
source, phase-contrast imaging at $\SI{85}{\kilo\electronvolt}$ has been
reported. Using a low-brilliance X-ray tube, Talbot-Lau interferometry was
applied at $\SI{60}{\kilo\electronvolt}$ mean energy \cite{Donath2009}.
Medical imaging applications may benefit from phase contrast at higher
energies: chest or abdominal
radiography or \ac{CT} require energies between $100$ and
$\SI{150}{\kilo\electronvolt}$. Other potential applications are homeland
security or chip failure analysis, which require high energies for the
visualization of materials of high density and atomic number.

Here, we introduce a method for phase-contrast imaging which is
compatible with the entire diagnostic energy range of X-rays. Moreover, the
method is fully compatible with compact imaging arrangements based on
conventional X-ray tubes. The method is based on Talbot-Lau interferometry
\cite{Pfeiffer2006} and employs an edge-on approach for the grating design and
arrangement. Up to now, Talbot-Lau interferometry has been applied with a
maximum design energy of $\SI{60}{\kilo\electronvolt}$ \cite{Donath2009}.
The challenge which limited the progress towards higher energies was mainly
related to the manufacturing of gratings with high aspect ratios. The aspect
ratio, given by
\begin{equation}
    \text{AR} = \frac{2h}{p},
\end{equation}
where $p$ is the grating period and $h$ the grating structure
height, is normally limited by the lithographic process, as grating
structures tend to collapse or to deform (e.g. through capillary forces) if
the aspect ratio is too high. For a given setup distance these parameters
depend on the target energy $E$ according to $p \propto
1/\sqrt{E}$ and $h \propto E^3$, and therefore $\textnormal{AR}
\propto E^{7/2}$\cite{Momose2003a}. If at $E=\SI{25}{\kilo\electronvolt}$ an aspect ratio
for the absorption grating of around $\textnormal{AR}=30$ is necessary for a
reasonable length of the experimental arrangement, it would have to be at
least $128$ for $E=\SI{100}{\kilo\electronvolt}$. Moreover, when using a
broad spectrum, photons above the design energy should also be
efficiently attenuated by the gratings, which requires even higher aspect ratios.
Maximum achievable aspect ratios of current grating fabrication techniques
\cite{David2007,Kenntner2010} are approximately around 60,
larger values are often not achievable or come at the expense of a very poor
grating quality and performance.

Our design introduces the edge-on
illumination of circularly aligned structures. Edge-on illumination
(figure~\ref{Fig:schematic}), as
opposed to face-on illumination, exploits the dimension along the grating
lines to form a high aspect ratio of the structures in direction of the beam. The
effective structure height of the grating is then determined by the grating
dimension along the grating lines, which essentially allows arbitrarily high
aspect ratios. 
\begin{figure}[ht]
    \includegraphics[width=\linewidth]{figures/figure1.eps}
    \caption{Schematic of a grating
        interferometer for X-ray energies between 60 and
        \SI{150}{\kilo\electronvolt} in edge-on illumination mode. The
        aspect ratio is defined by the ratio of the travelling distance along the
        grating lines and the period and can be arbitrarily long. In order to avoid
        a reduction of the field of view, the grating structures are aligned on an
    arc.}
    \label{Fig:schematic}
\end{figure}

@@

Grating design and fabrication is nonstandard and involves a complex mask
design, as shown in Figure~\ref{Fig:grating_mask}. Each grating resides on a
silicon chip and has its specific structure length and curvature. For the
current experiments, a symmetric interferometer with a grating period of $p
= \SI{2.8}{\micro\metre}$ for all gratings has been used. The design energy
is $\SI{100}{\kilo\electronvolt}$ and the beam splitter grating periodically
shifts the phase by zero and $\pi$ at this energy \cite{David2002}. Using
gold as the phase shifting material, this requires a structure length of
$h_1 = \SI{19.8}{\micro \metre}$. The analyzer grating is an absorption mask
for sensing slight changes of the interference pattern generated by the beam
splitter \cite{Momose2003a}. With a structure length of $h_2 =
\SI{800}{\micro \metre}$, this grating has an aspect ratio of $2h/p \approx
570$ and thus sufficiently attenuates X-rays up to energies of 
$\SI{160}{\kilo\electronvolt}$. Beam splitter- and analyzer grating are
separated at the first fractional Talbot order \cite{Weitkamp2005},
resulting in an intergrating distance of $\SI{158}{\milli\metre}$. The
source grating splits the relatively large focal spot ($\sim
\SI{1}{\milli\metre}$) into an array of individually coherent, but mutually
incoherent sources \cite{Pfeiffer2006}. It is also made of gold structures
with a structure length of $h_0 = h_2 = \SI{800}{\micro \metre}$.
\begin{figure} [ht]
    \includegraphics[width=\linewidth]{figures/grating_mask.eps}
    \caption{Grating design mask for
        the edge-on illumination approach. (a) Top part of the 4 inch wafer,
        showing five grating chips; one source grating, two beam splitter
        gratings and two analyzer gratings (from top to bottom). The
        gratings have different curvatures which are specific to the grating
        interferometer geometry. (b) Zoom into the grating structures,
        contain interrupting bridges used for stabilizing the grating
        structures in the lithographic process \cite{Kenntner2010}.}
        \label{Fig:grating_mask}
\end{figure}

@@

Fig.~\ref{Fig:img_chip} shows a radiographic scan of an electronic chip.
Several resistors and an integrated circuits are located on different layers
on the chip. The images were acquired in scanning mode, using a step size of
$\SI{100}{\micro \metre}$ along the $y$ axis. For a better comparison of the
magnified phase and attenuation images, the attenuation image has been
replaced with the differential attenuation image, which was obtained by
digital differentiation. In the attenuation image, the soldering points of
the integrated circuit are hardly visible underneath the resistors, while in
the phase image, they can clearly be identified. This shows the
benefit of the differential nature of the phase-contrast image, which may be
useful to identify flaws in multi-layered structures such as electronic
chips.
\begin{figure}[ht]
    \includegraphics[width=\linewidth]{figures/img_chip_dabs.eps}
    \caption{Radiographic scan of an electronic chip. The image was acquired
        with 24 phase steps and an exposure time of \SI{15}{\second} per
    step.}
    \label{Fig:img_chip}
\end{figure}

@@

In Fig.~\ref{Fig:img_chip}, image acquisition involved 24 phase steps
\cite{Weitkamp2005} and an exposure time of 15 seconds per step.

\section*{Acknowledgements} We thank Gordan Mikuljan from Paul Scherrer
Institute, Switzerland, for his work on the mechanical design, Joachim
Schulz and Marco Walter from Micro Works GmbH, Germany, for the competent
support on grating design issues, Christian Kottler and Vincent Revol from
Centre Suisse d'Electronique et de Microtechnique (CSEM), Switzerland for
the fruitful discussions on the design of the system.

>>>>

%\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress,groupedaddress]{revtex4}
%% for review and submission
%\documentclass[aps,preprint,showpacs,superscriptaddress,groupedaddress]{revtex4}
% for double-spaced preprint
%\documentclass[aps,prl,floatfix,twocolumn,10pt]{revtex4-1}
%for review and submission
\documentclass[aps,prl,preprint]{revtex4-1} 
% for double-spaced preprint
%\documentclass[aip,apl,amsmath,amssymb,floatfix,preprint,a4paper]{revtex4-1}
%\documentclass[aip,apl,amsmath,amssymb,floatfix,reprint,a4paper]{revtex4-1}

@@

%% ----------------------------------------------------------------------------------------------------------------
\begin{abstract}
    Phase contrast imaging with X-rays provides access to
    complementary physical contrast mechanisms. Phase sensitive imaging in
    the diagnostic energy range between $80$ and
    $\SI{150}{\kilo\electronvolt}$ is still largely unexplored, as the
    current methods typically entail severe technical challenges. A
    phase-contrast technique at such high energies is of scientific and
    industrial interest as it vastly expands the range of applications, for
    instance, by the examination of materials of high density or thickness.
    The approach includes a new design for the grating manufacturing in
    Talbot-Lau interferometry, with an edge-on illumination and curved
    structures to match the beam divergence. The edge-on approach breaks the
    current limits of achievable grating aspect ratios, which has been a key
    issue for a long time. The curvature of the gratings solves the
    intrinsic reduction of the field of view which occurs for gratings with
    such high aspect ratios and allows for a very compact setup, with a
    distance of \SI{31}{\centi\metre} between the source grating and the
    analyzer grating. Using an imaging arrangement based on a
    conventional X-ray tube, phase and dark-field contrast imaging at
    $\SI{100}{\kilo\electronvolt}$ is demonstrated. This achievement paves
    the road for the transfer of phase-contrast imaging into fields where
    high energies are required, such as medical computed tomography, chip
    failure analysis or homeland security.
\end{abstract}

@@

Talbot interferometry has been demonstrated using a synchrotron source at
$\SI{82}{\kilo\electronvolt}$ \cite{Willner2013} and
$\SI{123}{\kilo\electronvolt}$\cite{Ruiz2013}.
Using a low-brilliance X-ray tube, Talbot-Lau interferometry was
applied at $\SI{60}{\kilo\electronvolt}$ mean energy \cite{Donath2009}.
Medical imaging applications may benefit from phase contrast at higher
energies: chest or abdominal
radiography or \ac{CT} require energies between $100$ and
$\SI{150}{\kilo\electronvolt}$. Other potential applications are homeland
security or chip failure analysis, which require high energies for the
visualization of materials of high density and atomic number.

Here, we introduce a method for phase-contrast imaging which is
compatible with the entire diagnostic energy range of X-rays. Moreover, the
method is fully compatible with compact imaging arrangements based on
conventional X-ray tubes. The method is based on Talbot-Lau interferometry
\cite{Pfeiffer2006} and employs an edge-on approach for the grating design and
arrangement. 
The challenge which limited the progress towards higher energies was mainly
related to the manufacturing of gratings with high aspect ratios. The aspect
ratio, given by
\begin{equation}
    \text{AR} = \frac{2h}{p},
\end{equation}
where $p$ is the grating period and $h$ the grating structure
height, is normally limited by the lithographic process, as grating
structures tend to collapse or to deform (e.g. through capillary forces) if
the aspect ratio is too high. For a given setup distance these parameters
depend on the target energy $E$ according to $p \propto
1/\sqrt{E}$ and $h \propto E^3$, and therefore $\textnormal{AR}
\propto E^{7/2}$\cite{Momose2003a}. If at $E=\SI{25}{\kilo\electronvolt}$ an aspect ratio
for the absorption grating of around $\textnormal{AR}=30$ is necessary for a
reasonable length of the experimental arrangement, it would have to be at
least $128$ for $E=\SI{100}{\kilo\electronvolt}$. Moreover, when using a
broad spectrum, photons above the design energy should also be
efficiently attenuated by the gratings, which requires even higher aspect ratios.
Maximum achievable aspect ratios of current grating fabrication techniques
\cite{David2007,Kenntner2010} are approximately around 60,
larger values are often not achievable or come at the expense of a very poor
grating quality and performance.

Our design introduces the edge-on
illumination of circularly aligned structures. Edge-on illumination
(figure~\ref{Fig:schematic}), as
opposed to face-on illumination, exploits the dimension along the grating
lines to form a high aspect ratio of the structures in direction of the beam. The
effective structure height of the grating is then determined by the grating
dimension along the grating lines, which essentially allows arbitrarily high
aspect ratios. 
\begin{figure}[ht]
    \includegraphics[width=.5\textwidth]{figures/figure1.eps}
    \caption{Schematic of a grating
        interferometer for X-ray energies between 60 and
        \SI{150}{\kilo\electronvolt} in edge-on illumination mode. The
        aspect ratio is defined by the ratio of the travelling distance along the
        grating lines and the period and can be arbitrarily long. In order to avoid
        a reduction of the field of view, the grating structures are aligned on an
    arc.}
    \label{Fig:schematic}
\end{figure}

@@

Grating design and fabrication is nonstandard and involves a complex mask
design, as shown in Figure~\ref{Fig:grating_mask}. Each grating resides on a
silicon chip and has its specific structure length and curvature. For the
current experiments, a symmetric interferometer with a grating period of $p
= \SI{2.8}{\micro\metre}$ for all gratings has been used. The design energy
is $\SI{100}{\kilo\electronvolt}$ and the beam splitter grating periodically
shifts the phase by zero and $\pi$ at this energy \cite{David2002}. Using
gold as the phase shifting material, this requires a structure length of
$h_1 = \SI{19.8}{\micro \metre}$. The analyzer grating is an absorption mask
for sensing slight changes of the interference pattern generated by the beam
splitter \cite{Momose2003a}. With a structure length of $h_2 =
\SI{800}{\micro \metre}$, this grating has an aspect ratio of $2h/p \approx
570$ and thus sufficiently attenuates X-rays up to energies of 
$\SI{160}{\kilo\electronvolt}$. Beam splitter- and analyzer grating are
separated at the first fractional Talbot order \cite{Weitkamp2005},
resulting in an intergrating distance of $\SI{158}{\milli\metre}$. The
source grating splits the relatively large focal spot ($\sim
\SI{1}{\milli\metre}$) into an array of individually coherent, but mutually
incoherent sources \cite{Pfeiffer2006}. It is also made of gold structures
with a structure length of $h_0 = h_2 = \SI{800}{\micro \metre}$.
\begin{figure} [ht]
    \includegraphics[width=.5\textwidth]{figures/grating_mask.eps}
    \caption{Grating design mask for
        the edge-on illumination approach. (a) Top part of the 4 inch wafer,
        showing five grating chips; one source grating, two beam splitter
        gratings and two analyzer gratings (from top to bottom). The
        gratings have different curvatures which are specific to the grating
        interferometer geometry. (b) Zoom into the grating structures,
        contain interrupting bridges used for stabilizing the grating
        structures in the lithographic process \cite{Kenntner2010}.}
        \label{Fig:grating_mask}
\end{figure}

@@

Fig.~\ref{Fig:img_chip} shows a radiographic scan of an electronic chip.
Several resistors and an integrated circuits are located on different layers
on the chip. The images were acquired in scanning mode, using a step size of
$\SI{100}{\micro \metre}$ along the $y$ axis. For a better comparison of the
magnified phase and attenuation images, the attenuation image has been
replaced with the differential attenuation image, which was obtained by
digital differentiation. In the attenuation image, the contrast of the soldering points of
the integrated circuit is reduced underneath the resistors, while in
the phase image, they can clearly be identified. This shows the
benefit of the phase nature of the image, which may be
useful to identify flaws in multilayered structures such as electronic
chips.
\begin{figure}[ht]
    \includegraphics[width=.5\textwidth]{figures/img_chip_dabs.eps}
    \caption{Radiographic scan of an electronic chip. The image was acquired
        with 24 phase steps and an exposure time of \SI{15}{\second} per
    step. The top right image shows the differential absorption image.}
    \label{Fig:img_chip}
\end{figure}

@@

In Fig.~\ref{Fig:img_chip}, image acquisition involved 24 phase steps
\cite{Weitkamp2005} and an exposure time of 15 seconds per step. The long
exposure times are mostly constrained by the low average visibility of the
gratings (\SI{5}{\percent}). As the quality in the manufacturing of the
structure increases, the exposure time can become substantially shorter.

\section*{Acknowledgements} We thank Gordan Mikuljan from Paul Scherrer
Institute, Switzerland, for his work on the mechanical design, Joachim
Schulz and Marco Walter from Microworks GmbH, Germany, for the competent
support on grating design issues, Christian Kottler and Vincent Revol from
Centre Suisse d'Electronique et de Microtechnique (CSEM), Switzerland for
the fruitful discussions on the design of the system.
Part of this work has been supported by the ERC Grant ERC-2012-StG 310005-PhaseX.
